Computing Entropies With Nested Sampling

### 2017-07-10 paper/ms.tex
Writing about proposals

I ran the algorithm and computed the depth using a tolerance of
$L=10^{-3}\sqrt{100}$, so that the RMS difference between
points in the two datasets was about $10^{-3}$.
From the algorithm, the average depth was
\begin{align}
\depth_{\boldsymbol{x}} &= 698.25 \pm 0.34.
\end{align}
The log-volume of a 100-dimensional ball of radius
$L=10^{-3}\sqrt{100}$ is
$-551.76$. Therefore, the differential entropy is estimated to be
\begin{align}
H(\boldsymbol{x}) &\approx 146.49 \pm 0.34.
\end{align}
which is very close to the true value (suspiciously close, but this
was just a fluke).

@@

>>>>

I ran the algorithm and computed the depth using a tolerance of
$L=10^{-3}\sqrt{100}$, so that the RMS difference between
points in the two datasets was about $10^{-3}$.
From the algorithm, the average depth was
\begin{align}
\depth_{\boldsymbol{x}} &= 698.25 \pm 0.34.
\end{align}
The log-volume of a 100-dimensional ball of radius
$L=10^{-3}\sqrt{100}$ is
$-551.76$. Therefore, the differential entropy is estimated to be
\begin{align}
H(\boldsymbol{x}) &\approx 146.49 \pm 0.34.
\end{align}
which is very close to the true value (perhaps suspiciously close, but this
was just a fluke).

To carry out the sampling for this problem, Metropolis-Hastings moves that
explore the joint prior distribution $p(\mu, \boldsymbol{x})$ had to be
implemented. Four basic kinds of proposals were used: i) those which change
$\mu$ while leaving $\boldsymbol{x}$ fixed; ii) those which change $\mu$ and
shift $\boldsymbol{x}$ correspondingly; iii) those which resample a subset
of the $x$s from $p(\boldsymbol{x}|\mu)$; and iv) those which move a single
$x$ slightly.

@@

To carry out the sampling for this problem, Metropolis-Hastings moves that
explore the joint prior distribution $p(A, \tau, \phi, \boldsymbol{d})$
had to be
implemented. As with the first example, there were four basic kinds of
proposals. Four basic kinds of proposals were used: i) those which change
one of the parameters
$A$, $\tau$ or $\phi$ while leaving $\boldsymbol{x}$ fixed
(these are standard Metropolis moves targeting the posterior distribution);
ii) those which change the parameters and modify the data accordingly;
iii) those which resample a subset
of the data; and iv) those which move a single datum slightly.
